---
title: "MJAC & #MeToo"
subtitle: "Tracking the Early Tweets"
author: "Cillian McHugh"
date: "8th May 2020"
bibliography: "../../Research_general/resources/bib/My Library.bib"
csl: "../../Research_general/apa.csl"
output:
  bookdown::html_document2:
    fig_caption: yes
    toc: true
    toc_float:
      toc_collapsed: false
    toc_depth: 4
    number_sections: false
editor_options: 
  chunk_output_type: console
---

```{=html}
<script>
$(document).ready(function() {
  $items = $('div#TOC li');
  $items.each(function(idx) {
    num_ul = $(this).parentsUntil('#TOC').length;
    $(this).css({'text-indent': num_ul * 10, 'padding-left': 10});
  });

});
</script>
```
```{=html}
<style type="text/css">
  .table-container {
  width: 100%;
  overflow-x: scroll;
}
</style>
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(include = FALSE)
```

```{r loadlibraries}
install.packages("devtools")
devtools::install_github("crsh/papaja")
devtools::install_github("cjbarrie/academictwitteR")
devtools::install_github("cillianmiltown/R_desnum")

library(papaja)

library(desnum)
library(tidyverse)
library(academictwitteR)
#install.packages("DT")
library(DT)
library(kableExtra)



```

```{r, include=FALSE}

load("twitter_dev_credentials.RData")

```

## 1st October 2017

```{r}

tweets <-
  get_all_tweets(
    "#MeToo",
    "2017-10-01T00:00:00Z",
    "2017-10-02T00:00:00Z",
    bearer_token,
    file = "downloaded_tweets/meetootweets"
  )
```

```{r}
date <- (1)
number_of_tweets <- length(tweets$text)
tot1 <- data.frame(date,number_of_tweets)
tot <- tot1
```

Total number of tweets = `r number_of_tweets`.

::: {.table-container}
```{r, include=TRUE}
datatable(tweets)
```
:::

## 2nd October 2017

```{r}
tweets <-
  get_all_tweets(
    "#MeToo",
    "2017-10-02T00:00:00Z",
    "2017-10-03T00:00:00Z",
    bearer_token,
    file = "downloaded_tweets/meetootweets"
  )
```

```{r}
date <- (2)
number_of_tweets <- length(tweets$text)
tot2 <- data.frame(date,number_of_tweets)
tot <- rbind(tot, tot2)
```

Total number of tweets = `r number_of_tweets`.

::: {.table-container}
```{r, include=TRUE}
datatable(tweets)
```
:::

## 3rd October 2017

```{r}
tweets <-
  get_all_tweets(
    "#MeToo",
    "2017-10-03T00:00:00Z",
    "2017-10-04T00:00:00Z",
    bearer_token,
    file = "downloaded_tweets/meetootweets"
  )
```

```{r}
date <- (3)
number_of_tweets <- length(tweets$text)
tot2 <- data.frame(date,number_of_tweets)
tot <- rbind(tot, tot2)
```

Total number of tweets = `r number_of_tweets`.

::: {.table-container}
```{r, include=TRUE}
datatable(tweets)
```
:::

## 4th October 2017

```{r}
tweets <-
  get_all_tweets(
    "#MeToo",
    "2017-10-04T00:00:00Z",
    "2017-10-05T00:00:00Z",
    bearer_token,
    file = "downloaded_tweets/meetootweets"
  )
```

```{r}
date <- (4)
number_of_tweets <- length(tweets$text)
tot2 <- data.frame(date,number_of_tweets)
tot <- rbind(tot, tot2)
```

Total number of tweets = `r number_of_tweets`.

::: {.table-container}
```{r, include=TRUE}
datatable(tweets)
```
:::

## 5th October 2017

```{r}
tweets <-
  get_all_tweets(
    "#MeToo",
    "2017-10-05T00:00:00Z",
    "2017-10-06T00:00:00Z",
    bearer_token,
    file = "downloaded_tweets/meetootweets"
  )
```

```{r}
date <- (5)
number_of_tweets <- length(tweets$text)
tot2 <- data.frame(date,number_of_tweets)
tot <- rbind(tot, tot2)
```

Total number of tweets = `r number_of_tweets`.

::: {.table-container}
```{r, include=TRUE}
datatable(tweets)
```
:::

## 6th October 2017

```{r}
tweets <-
  get_all_tweets(
    "#MeToo",
    "2017-10-06T00:00:00Z",
    "2017-10-07T00:00:00Z",
    bearer_token,
    file = "downloaded_tweets/meetootweets"
  )
```

```{r}
date <- (6)
number_of_tweets <- length(tweets$text)
tot2 <- data.frame(date,number_of_tweets)
tot <- rbind(tot, tot2)
```

Total number of tweets = `r number_of_tweets`.

::: {.table-container}
```{r, include=TRUE}
datatable(tweets)
```
:::

## 7th October 2017

```{r}
tweets <-
  get_all_tweets(
    "#MeToo",
    "2017-10-07T00:00:00Z",
    "2017-10-08T00:00:00Z",
    bearer_token,
    file = "downloaded_tweets/meetootweets"
  )
```

```{r}
date <- (7)
number_of_tweets <- length(tweets$text)
tot2 <- data.frame(date,number_of_tweets)
tot <- rbind(tot, tot2)
```

Total number of tweets = `r number_of_tweets`.

::: {.table-container}
```{r, include=TRUE}
datatable(tweets)
```
:::

## 8th October 2017

```{r}
tweets <-
  get_all_tweets(
    "#MeToo",
    "2017-10-08T00:00:00Z",
    "2017-10-09T00:00:00Z",
    bearer_token,
    file = "downloaded_tweets/meetootweets"
  )
```

```{r}
date <- (8)
number_of_tweets <- length(tweets$text)
tot2 <- data.frame(date,number_of_tweets)
tot <- rbind(tot, tot2)
```

Total number of tweets = `r number_of_tweets`.

::: {.table-container}
```{r, include=TRUE}
datatable(tweets)
```
:::

## 15th October 2017

```{r}
tweets <-
  get_all_tweets(
    "#MeToo",
    "2017-10-15T00:00:00Z",
    "2017-10-16T00:00:00Z",
    bearer_token,
    file = "downloaded_tweets/meetootweets"
  )
```

```{r}
date <- (15)
number_of_tweets <- length(tweets$text)
tot2 <- data.frame(date,number_of_tweets)
tot <- rbind(tot, tot2)
```

Total number of tweets = `r number_of_tweets`.

::: {.table-container}
```{r, include=TRUE}
datatable(tweets)
```
:::
